Hydras \& Co.

### 2022-11-18 doc/chapter-fol.tex
experimental notations

In order to get more readable terms and formulas, we can define a few notations in ~\href{../theories/html/hydras.Ackermann.LNN.html}{Ackermann.LNN}

@@

>>>>

@@

\section{Notations for Formulas (experimental)}

In order to get more readable terms and formulas, we can define a few notations in ~\href{../theories/html/hydras.MoreAck.FOL_notations.html}{MoreAck.FOL\_notations} and
~\href{../theories/html/hydras.Ackermann.LNN_notations.html}{MoreAck.LNN\_notations}.

\section{Proofs}

\subsection{Contexts as lists}

\begin{exercise}

Prove the following lemma:
\inputsnippets{fol_Examples/eqRefl}

\end{exercise}

\subsection{Contexts as sets}

\begin{exercise}

Prove the following lemma:
\inputsnippets{fol_Examples/MPdiag}

\end{exercise}
